---
title: "Total Factor Productivity production process"
author: "David Lee"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Total Factor Productivity production process}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(tidyverse)
library(TFP)

```

##Annual Business Survey data

###1. Update the ABS data

1. Get the latest ABS data from ONS. The latest release can be found [here](https://www.ons.gov.uk/businessindustryandtrade/business/businessservices/bulletins/uknonfinancialbusinesseconomy/previousReleases). The spreadsheet we need is the one for [Sections A - S](https://www.ons.gov.uk/businessindustryandtrade/business/businessservices/datasets/uknonfinancialbusinesseconomyannualbusinesssurveysectionsas/current).
2. The spreadsheet needs to be manually adjusted to impute suppressed values before proceeding.
3. Then collate the latest data for a sector using `ABS`.
4. Historic ABS data is included in the package dataset `abs_historic`. 
5. Add the latest data to `abs_historic`, removing any duplicate years. 

```{r abs_processing, warning=FALSE}
# ABS workflow

# reshape the historic data
abs_hist <- abs_historic %>% 
               filter(sector == "food manufacturing") %>% 
               select(-c(sector, sic_desc)) %>% 
               gather(year, val, num_range("", 1900:2100)) %>% 
               spread(attribute, val) %>% 
               mutate(year = as.numeric(year))

head(abs_hist)

# read in the latest
manufacturing <- ABS(file = "~/TFP_code/data/abssectionsas.xls",
                     sheets = c("Section C"),
                     siccodes = c("10", "11")) %>% 
                select(year, capex, employment_costs, employment_pit, gva, purchases, turnover)

head(manufacturing)

# bind the latest data to the older data
manu_latest <- abs_hist %>% 
                   filter(year < min(manufacturing$year)) %>% 
                   bind_rows(manufacturing)


```

###2. update the input weights

1. We can produce the latest input weights using `input_weights` on the ABS data we produced in section 1. Note that `input_weights` produces a dataset with no year variable. We might want to add one.

```{r input_weights}

iw <- input_weights(manu_latest, capex, purchases, employment_costs)
iw$year <- min(manu_latest$year):max(manu_latest$year)

head(iw)

```


$\sqrt\frac{onething}{another}$

